Statistical Analysis

### 2024-04-15 code/analysis-code/statistical-analysis.qmd
Part 4 Updates
Added method descriptions in the supplemental file and wrote instructions for reproducibility. Updated manuscript with code processing summary and CV/bootstrapping explanations.
Removed ANOVA and Tukey.
Changed lmfit9 to null model

### ANOVA for region variable
We want to compare the mean percent of unintended pregnancies among those using short acting reversible methods across the five regions: Asia, Africa, Europe, Latin America and the Caribbean, and Oceania. We will start with an ANOVA test to determine the relationship between region and outcome. We are more interested in pairwise comparisons between the regions, so we also conducted Tukey's Honestly Significant Difference test for pairwise comparisons within ANOVA. 
```{r}
# conduct an ANOVA test with the region variable
regionANOVA <- aov(pct_upreg_sarc ~ region, data = mydata)

# explore ANOVA results 
summary(regionANOVA)

# add Tukey's HSD test for pairwise comparisons
tukey_result <- TukeyHSD(regionANOVA)

# explore the pairwise comparisons
tidy(tukey_result)

# save fit results table  
table_file13 = here("results", "tables", "resulttable13.rds")
saveRDS(tukey_result, file = table_file13)
```
ANOVA results show that the region variable is statistically significantly associated with the outcome variable given the p-value less than 0.001. The Tukey HSD test revealed the largest differences in the outcome between the Oceania region and Latin America/the Caribbean, Europe, and Asia. The relationships between Oceania and Europe and Latin America/the Caribbean are statistically significant with p-values less than 0.0001. Oceania is clearly experiencing the lowest percentage of unintended pregnancies among short acting reversible method users.  The lowest difference in outcome between regions is between Asia and Africa, but this is not a statistically significant association. Two statistically significant differences in the outcome exist between Latin America/the Caribbean and Europe with Africa, which shows that Africa is experiencing higher levels of the outcome.

@@

# create predictions using the null model
nullpred <- predict(lmfit9, new_data = mydata) %>% 
                  select(.pred)

@@

>>>>

@@

# create predictions using the null model
nullpred <- predict(null_model, new_data = mydata) %>% 
                  select(.pred)

@@

We are considering adding a random forest model to further examine the variance in our model.
